Inferring generation-interval distributions from contact tracing data: \\ \emph{in prep, PRSB}

### 2018-11-12 doc/network.tex
lots of files

>>>>

\section{Appendix}

These are notes for now ... Need to move them elsewhere and change notation... but this is part of our figure for empirical network ...

$$
1 = \kappa \phi_L(\alpha) \frac{\lambda^{(net)}}{\alpha + \lambda^{(net)}} (1 - \phi_I(\alpha+\lambda^{(net)}))
$$
where in our specific example,
$$
\phi_L(\alpha) = \frac{4 \delta^2}{(2 \delta + \alpha)^2}
$$
and so we have
$$
1 = \frac{4 \delta^2}{(2 \delta + \alpha)^2} \frac{\kappa \lambda^{(net)}}{\lambda^{(net)} + \alpha + \gamma},
$$
which suggests that
$$
\lambda^{(net)} = \frac{(2\delta + \alpha)^2 (\alpha + \gamma)}{(\kappa - 1) 4 \delta^2 - 4 \delta \alpha - \alpha^2}
$$
We can substitute into the following equation to obtain the $r$ and $\RR$ relationship:
$$
\RR = \kappa \frac{\lambda^{(net)}}{\lambda^{(net)} + \gamma}
$$
